---
title: "DDP course project"
author: "David Lennox-Hvenekilde"
date: "20/02/2022"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

## Mapping the Biotech industry ecosystem in Denmark
Denmark has an history of innovation in life sciences, compared to it's small size. In this project for *Developing Data Products: R Markdown and Leaflet*.  This is of interest to me, as I current work as a Scientist in a Danish Biotech company. Here i will map the physical locations of Danish Biotechnology companies, in Denmark


### Data used
The dataset for this project has been scraped from [Proff.dk](https://proff.dk), which is a Danish website that shows information about all registered Danish companies. You can search companies by Industry. You have to may to get the data in a .csv file, and they do not have latitude/longitude for the companies. This means that some effort was put into retrieving and cleaning the data to make it useful, and the data gathering actually took ~10 times longer than making this simple RMD file. You can see how the data retrieval/cleaning was done in the a separate R file: [DDPcourseproject_datascrape.R](https://github.com/DavidL-H/Biotech-in-Denmark/blob/main/DDPcourseproject_datascrape.R). We will just read the .csv file that is the output of this script:

```{r BiotechData}
urlfile<-'https://raw.githubusercontent.com/DavidL-H/Biotech-in-Denmark/main/Biotech_companies_Denmark.csv'
BiotechCompanies<-read.csv(urlfile)
BiotechCompanies <- BiotechCompanies[,-1]
colnames(BiotechCompanies)<-c("Company", "Address", "lng", "lat")
head(BiotechCompanies)
```

### Mapping Danish Biotech companies:
Now we have the data we want, and we can easily map it with the package leaflet():

```{r linkedin}
library(leaflet)
library(dplyr)
BiotechCompanies %>%
  leaflet()%>%
  addTiles()%>%
  addMarkers(clusterOptions = markerClusterOptions(),
             popup = BiotechCompanies$Company)
```