---
title: "DDP course project"
author: "David Lennox-Hvenekilde"
date: "12/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Mapping the Synthetic Biology start-up ecosystem in Denmark
Denmark has an history of innovation in life sciences, compared to it's small size. This has historically been driven largely by veritable pharmaceutical giants like Novo Nordisk. Recently, more focus is being put on the use of Biology to solve other societal issues. This includes replacing traditional fossil fuel-based chemical and fuel manufacturing (Industrial Biotechnology) or food production (Food Biotechnology). To achieve this, one need harness the power of biology to redesign living organisms, often refereed to as Synthetic Biology. While the definition of synthetic biology can be fluid, in this report it will be used as an umbrella term for high-tech biotechnology whose sole purpose is not pharmaceuticals. This will include "pick-an-shovel" companies that develop biological products or services aimed at the biotech industry.

Maybe star-ups and SMEs are a better name


### Goal of analysis
Create a dashboard for visualizing physical locations of Synthetic Biology start-up companies

### Resources used for analysis
* [Linkedin](https://Linkedin.com/) - Accesses via the API with [Rlinedin package](https://CRAN.R-project.org/package=Rlinkedin) 

* [Dansk Biotek](https://danskbiotek.dk/) - Trade organization specializing in Danish Biotechnology, including start-up companies.

```{r linkedin}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
